Unshuffling Permutations

### 2015-09-24 submission.tex
typos

Besides, a permutation $\pi$ is a {\em square} if there is a
permutation $\sigma$ such that $\pi$ appears in $\sigma \SHUFFLE \sigma$.
In this case, we say that $\sigma$ is a {\em square root} of $\pi$.
Equivalently, $\pi$ is a square with $\sigma$ as square root if and only
if in the expansion of $\Delta(\pi)$, there is a tensor
$\sigma \otimes \sigma$ with a nonzero coefficient. In a more
combinatorial way, this is equivalent to say that there are two sets
$P_1$ and $P_2$ of disjoints indexes of letters of $\pi$ satisfying
$P_1 \sqcup P_2 = [|\pi|]$ such that the subword $\pi_{|P_1}$ and
$\pi_{|P_2}$ are order-isomorphic. Computer experiments give us the
first numbers of square permutations with respects to their size, which
are, from size $0$ to $10$,
\begin{equation}
    1, 0, 2, 0, 20, 0, 504, 0, 21032, 0, 1293418.
\end{equation}
This sequence (and its subsequence obtained by removing the $0$s) is for
the time being not listed in~\cite{Slo}. The square permutations of
sizes $0$ to $4$ are
\smallskip

>>>>

Besides, a permutation $\pi$ is a {\em square} if there is a
permutation $\sigma$ such that $\pi$ appears in $\sigma \SHUFFLE \sigma$.
In this case, we say that $\sigma$ is a {\em square root} of $\pi$.
Equivalently, $\pi$ is a square with $\sigma$ as square root if and only
if in the expansion of $\Delta(\pi)$, there is a tensor
$\sigma \otimes \sigma$ with a nonzero coefficient. In a more
combinatorial way, this is equivalent to say that there are two sets
$P_1$ and $P_2$ of disjoints indexes of letters of $\pi$ satisfying
$P_1 \sqcup P_2 = [|\pi|]$ such that the subwords $\pi_{|P_1}$ and
$\pi_{|P_2}$ are order-isomorphic. Computer experiments give us the
first numbers of square permutations with respects to their size, which
are, from size $0$ to $10$,
\begin{equation}
    1, 0, 2, 0, 20, 0, 504, 0, 21032, 0, 1293418.
\end{equation}
This sequence (and its subsequence obtained by removing the $0$'s) is for
the time being not listed in~\cite{Slo}. The square permutations of
sizes $0$ to $4$ are
\smallskip
